Creation of a corpus of realistic urban sound scenes with controlled acoustic properties

### 2017-06-19 boston-presentation.tex
fex fixes

\title[Acoustics'17 Boston]{Creation of a corpus of realistic urban sound scenes with controlled acoustic properties}
\author[J. Gloaguen]{\emph{Jean-R\'emy Gloaguen}$^1$,  Arnaud Can$^1$,\\ Mathieu Lagrange$^2$,  Jean-Fran\c cois Petiot$^2$}
\institute[Ifsttar]{$^1$French Institute of Science and Technology for Transport, Development and Networks, \\ Environmental Acoustics Laboratory \\Allée des Ponts et Chaussées, Route de Bouaye, - CS4, 44344 Bouguenais Cedex, FR  \\ \vspace{.25cm} $^2$Nantes' Numeric Sciences Laboratory, \\1, rue de la Noë, BP 92101, 44321 Nantes Cedex 3, FR}
\date[06/29/2017]{Acoustics' 17 Boston\\06/29/2017}

@@

\begin{itemize}
	\item Subject of many researches both on perceptual and physical aspects
	\item Based on real sound environments with \textit{soundwalks} or recordings listened on laboratory\\
	$\Rightarrow$ ecological validity \\
	$\Rightarrow$ no controlled framework \\
	$\Rightarrow$ no repeatable experience \\

@@

		$\Rightarrow$ controlled framework  \\
		$\Rightarrow$ creation of specific urban sound environments \\
		$\Rightarrow$ no ecological validity \\
\end{itemize}

@@

\begin{block}{Proposition}
\begin{itemize}
	\item Use real recordings to base the distribution of the events
	\item Validate the realism of the sound mixtures obtained with a perceptual test
\end{itemize}

@@

\begin{frame}{\textit{SimScene}: a web-simulator to design sound environments (REF)}
\begin{block}{Principe}
\begin{itemize}
	\item Superpose sound events and a background from an isolated sound database
	\item Control a set of high level parameters
	\begin{itemize}
		\item presence time and sound level of each sound class
		\item number of occurrence of a sound class
	\end{itemize}
	\item Standard deviation on each parameter to bring random behavior
	\item Generate a separate audio file for each sound class present\\
	$\Rightarrow$ enable to know their exact contribution

@@

\begin{block}{2 modes to design the sound mixtures}
\begin{itemize}
	\item \textit{abstract}: the user fills all the information 
	\item \textit{replicate}: the sound classes and the temporal position of each events come from an annotated text file
\end{itemize}
\end{block}

@@

\begin{block}{Constitution of the panel}
\begin{itemize}
	\item 18 females and 31 males (1 not documented)
	\item Average age : 36 ($\pm$ 12) years old
	\item 62 $\%$ of the participant declared having NO experience in the listening of urban sound mixtures
\end{itemize}
\end{block}

>>>>

\title[Acoustics'17 Boston]{Creation of a corpus of realistic urban sound scenes with controlled acoustic properties}
\author[J. Gloaguen]{\emph{Jean-R\'emy Gloaguen}$^1$,  Arnaud Can$^1$,\\ Mathieu Lagrange$^2$,  Jean-Fran\c cois Petiot$^2$}
\institute[Ifsttar]{$^1$French Institute of Science and Technology for Transport, Development and Networks, \\ Environmental Acoustics Laboratory \\Allée des Ponts et Chaussées, Route de Bouaye, - CS4, 44344 Bouguenais Cedex, FR  \\ \vspace{.25cm} $^2$ LS2N, \\1, rue de la Noë, BP 92101, 44321 Nantes Cedex 3, FR}
\date[06/29/2017]{Acoustics' 17 Boston\\06/29/2017}

@@

\begin{itemize}
	\item Subject of many researches both on perceptual and physical aspects
	\item Based on real sound environments with \textit{soundwalks} or recordings listened on laboratory\\
	$\Rightarrow$ good ecological validity \\
	$\Rightarrow$ no controlled framework \\
	$\Rightarrow$ no repeatable experience \\

@@

		$\Rightarrow$ controlled framework  \\
		$\Rightarrow$ creation of specific urban sound environments \\
		$\Rightarrow$ low ecological validity \\
\end{itemize}

@@

\begin{block}{Proposition}
\begin{itemize}
	\item Transcribe real recordings
	\item use the transcription to simulate controled stimuli
	\item Validate the realism of the simulated sound mixtures obtained with a perceptual test
\end{itemize}

@@

\begin{frame}{\textit{SimScene}: a simulator to design sound environments \footnote{\url{https://bitbucket.org/mlagrange/simscene}}}
\begin{block}{Principe}
\begin{itemize}
	\item Mix sound events and a background taken from an isolated sound database
	\item Control a set of high level parameters
	\begin{itemize}
		\item onset time and sound level of each sound class
		\item number of occurrence of a sound class
	\end{itemize}
	\item Standard deviation on each parameter to bring random behavior
	\item Generate a separate audio file for each sound class \\
	$\Rightarrow$ enable to know their exact contribution

@@

\begin{block}{2 modes to design the sound mixtures}
\begin{itemize}
	\item \textit{abstract}: the user sets abstract information (mean / variance)
	\item \textit{replicate}: the sound classes and the temporal position of each events come from an annotated text file
\end{itemize}
\end{block}

@@

\begin{block}{The panel}
\begin{itemize}
	\item 18 females and 31 males (1 not documented)
	\item Average age : 36 ($\pm$ 12) years old
	\item 62 $\%$ of the participant declared having NO experience in the listening of urban sound mixtures
\end{itemize}
\end{block}
